\Huge Conferences in the Era of Expensive Carbon

### 2019-06-05 main.tex
More writing

In the short term, one possible response to both questions is to use {\em
  carbon offsets}, which allow organizations (and individuals) to
voluntarily impose a price on their own emissions~\cite{CarbonOFfsetReport}.
%
In a nutshell, the idea is that a conference can raise funds from
registration fees or corporate sponsors and give them, via a carbon offset
{\em vendor}, to a {\em provider} who will use them to support an activity
(e.g., installing methane capture devices on landfill sites or buying
efficient cookstoves to replace open-fire cooking in developing areas) that
is {\em certified} (by yet another organization) to permanently avoid
emitting an amount of greenhouse gases equivalent to the emissions from
participants' travel to the conference.
%
Many organizations (including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and a number of academic societies) are already buying carbon offsets, and
some ACM conferences have already started to experiment with voluntary
carbon offset fees at registration time.

Carbon offsets do come with some significant concerns.
%
A superficial but potentially sigificant issue is that most
organizations do not currently have accounting procedures in place to deal
with them, and the piecemeal political and bureaucratic work of designing
and implementing a separate policy for each organization can consume
significant energy.
%
A more fundamental problem is that it is not straightforward to decide how
much it should cost to offset a ton of carbon: current prices vary widely
around an average of around \$15 per ton, depending on the vendor, the
nature of the offset project, the region of the world where it will be
implemented, etc..  Worse, in order for offsets (or any other form of a
carbon pricing) to fully motivate the needed changes in behavior, the price
may need to go much higher---the true ``social cost'' of a ton of carbon is
variously estimated at anywhere from \$40 to \$400 per
ton~\bcp{citation}---and setting it too low may encourage complacency.
%
And finally, 
%
We feel that, on balance, voluntary carbon offsetting can be an
effective tool for raising awareness and changing organizational behavior
in the short term.
%
Moreover, supporting well-chosen carbon mitigation activities has a clear
benefit in reducing global net emissions now.

>>>>

In the short term, one possible response to both questions is to use {\em
  carbon offsets}, which allow organizations (and individuals) to
voluntarily impose a price on their own emissions~\cite{CarbonOFfsetReport}.
%
In a nutshell, the idea is for a conference to raise funds from
registration fees or corporate sponsors and donate them, via a carbon offset
{\em vendor}, to a {\em provider} who will use them to support an activity
(e.g., installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities) that
is {\em certified} (by yet another organization) to permanently avoid
emitting an amount of greenhouse gases equivalent to the emissions from
participants' travel to the conference.
%
Many organizations (including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and a number of academic societies) are already buying carbon offsets, and
some ACM conferences have already started to experiment with voluntary
carbon offset fees at registration time.

Carbon offsets do come with some significant concerns.
%
One superficial impediment is that most organizations do not currently have
accounting procedures in place to deal with them, and the piecemeal
political and bureaucratic work of designing and implementing a separate
policy for each organization can consume significant energy.
%
Another point to be careful of is that the long-term climate benefit of some
offsetting strategies (for example, paying people to plant trees) is
controversial.
%
A more fundamental problem is that it is not straightforward to decide how
much one should pay to offset a ton of carbon: current prices vary widely
around an average of around \$15 per ton, depending on the vendor, the
nature of the offset project, the region of the world where it will be
implemented, etc.  Moreover, in order for offsets (or any other form of a
carbon pricing) to fully motivate the needed changes in behavior, the price
may need to go much higher---the true ``social cost'' of a ton of carbon is
variously estimated at anywhere from \$40 to \$400 per
ton~\bcp{citation}---and setting it too low may encourage complacency.
%
However, while acknowledging these concerns, we believe that voluntary
carbon offsetting can be an effective near-term tool for raising awareness
and beginning to shift organizational behavior because it associates
emissions with a number, giving decision makers within the organization
something concrete to optimize.
